---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# owidapi

<!-- badges: start -->
<!-- badges: end -->

 Retrieve datasets from Our World in Data (OWID) [Chart API and ETL Catalog API](https://docs.owid.io/projects/etl/api/).


## Installation

You can install the development version of `owidapi` from GitHub with:

``` r
# install.packages("pak")
pak::pak("tidy-intelligence/r-owidapi")
```

## Usage

Load the package:
```{r}
library(owidapi)
```

Download the full life expectancy dataset:

```{r}
owid_get("life-expectancy")
```

Get life expectancy data for Australia, Austria, and Germany:
```{r}
owid_get("life-expectancy", entities = c("AUS", "AUT", "GER"))
```

Download US life expectancy data from 1970 to 1980:

```{r}
owid_get("life-expectancy", entities = "USA", start_date = 1970, end_date = 1980)
```

Get daily COVID-19 vaccination doses per capita for Germany between 2020-12-28 and 2020-12-31:

```{r}
owid_get(
  "daily-covid-vaccination-doses-per-capita",
  entities = "DEU",
  start_date = "2020-12-28",
  end_date = "2020-12-31"
)
```

Download data directly using a URL:

```{r}
owid_get(
  url = paste0(
    "https://ourworldindata.org/grapher/civil-liberties-score-fh",
    "?tab=chart&time=earliest..2023&country=ARG~AUS~BWA~CHN~ALB~DEU"
  )
)
```
