---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# owidapi

<!-- badges: start -->
![R CMD Check](https://github.com/tidy-intelligence/r-owidapi/actions/workflows/R-CMD-check.yaml/badge.svg)
![Lint](https://github.com/tidy-intelligence/r-owidapi/actions/workflows/lint.yaml/badge.svg)
[![Codecov test coverage](https://codecov.io/gh/tidy-intelligence/r-owidapi/graph/badge.svg)](https://app.codecov.io/gh/tidy-intelligence/r-owidapi)
<!-- badges: end -->

 Retrieve datasets from Our World in Data (OWID) [Chart API](https://docs.owid.io/projects/etl/api/).

 The ETL Catalog API is currently in beta and relies on internal APIs that change on a regular basis. Once the API is stable, it will also be included in this package. 


## Installation

You can install the development version of `owidapi` from GitHub with:

``` r
# install.packages("pak")
pak::pak("tidy-intelligence/r-owidapi")
```

## Usage

Load the package:
```{r}
library(owidapi)
```

Download the full life expectancy dataset:

```{r}
owid_get("life-expectancy")
```

Get life expectancy data for Australia, Austria, and Germany:
```{r}
owid_get("life-expectancy", entities = c("AUS", "AUT", "GER"))
```

Download US life expectancy data from 1970 to 1980:

```{r}
owid_get("life-expectancy", entities = "USA", start_date = 1970, end_date = 1980)
```

Get daily COVID-19 vaccination doses per capita for Germany between 2020-12-28 and 2020-12-31:

```{r}
owid_get(
  "daily-covid-vaccination-doses-per-capita",
  entities = "DEU",
  start_date = "2020-12-28",
  end_date = "2020-12-31"
)
```

Download data directly using an URL:

```{r}
url <- paste0(
  "https://ourworldindata.org/grapher/civil-liberties-score-fh",
  "?tab=chart&time=earliest..2023&country=ARG~AUS~BWA~CHN~ALB~DEU"
)
owid_get(url = url)
```

You can get metadata as a list by either provoding the data set name or URL.
```{r}
metadata <- owid_get_metadata("civil-liberties-score-fh")
metadata_url <- owid_get_metadata(url = url)
str(metadata)
```

The only difference is in the `originalChartUrl` value:

```{r}
all.equal(metadata, metadata_url)
```
